\section*{
    \colorbox{gainsboro}{PATENTS}  
}

\begin{enumerate}[leftmargin=8mm,nosep]
    \item Data Exploration Using Natural Language With Data Sampling. US Patent App. 19/691,413.
    \item Multi-Agent Design System. US Patent App. 19/662,166.
    \item Axis-Based Variety In Generative Artificial Intelligence. US Patent App. 19/650,581.
    \item Scalable Usability Testing System Using Simulation Agents. US Patent App. 19/459,837.
    \item Generating Scalable Vector Graphic Images Bound To Insight-Backing Data. US Patent App. 18/933,259.
    \item Modularized And Extensible Framework For Visualization-To-Caption Generation. US Patent App. 18/663,531.
    \item Natural Language Query Filtering. US Patent App. 18/747,630.
    \item Digital Content Generation From A Text-Based Input. US Patent App. 18/594,376.
    \item Generation Of Data Story Recommendations Via Elicited User Feedback. US Patent App. 18/422,665.
    \item Generating Hierarchical Queries From Natural Language. US Patent App. 18/486,603.
    \item Performing Machine Learning Techniques For Hypertext Markup Language-Based Style Recommendations. US Patent App. 18/225,906.
    \item Hypergraph Representation Learning. US Patent App. 18/358,502.
    \item Generating Data Insights. US Patent App. 18/328,980.
    \item Approximate Query Processing For Join Queries. US Patent App. 18/092,779.
    \item Generating Editable Email Components Utilizing A Constraint-Based Knowledge Representation. US Patent App. 18/055,238.
    \item Systems And Methods For Document Generation. US Patent App. 17/809,371.
    \item Extensible Framework For Generating Accessible Captions For Data Visualizations. US Patent App. 17/656,254.
    \item Trait Expansion Techniques In Binary Matrix Datasets. US Patent App. 17/677,323.
    \item Dynamic Clustering Of Sparse Data Utilizing Hash Partitions. US Patent App. 16/852,110.
    \item Segmenting Users With Sparse Data Utilizing Hash Partitions. US Patent App. 17/660,328.
\end{enumerate}